Supplementary material for: \nA comparison of single-cell trajectory inference methods

### 2018-11-14 manuscript/supplementary.Rmd
remove toc files

---
title: "Supplementary material for: \nA comparison of single-cell trajectory inference methods"
output: 
  dynbenchmark::pdf_manuscript:
      render_change: FALSE
---

@@

```{r}
# dynbenchmark::knit_nest("../results/02-metrics/")
```

>>>>

---
title: "Supplementary material for: \nA comparison of single-cell trajectory inference methods"
output: 
  dynbenchmark::pdf_supplementary_note:
      render_change: FALSE
---

@@

```{r}
dynbenchmark::knit_nest("../results/02-metrics/")
```
